Algomusicology, ????, Profit

### 2016-05-29 paper.tex
Tidy references.

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
\bibitem{Anti EP} Autechre: Anti EP
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
\bibitem{Leipzig} Ford, Chris: Leipzig
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
\bibitem{Clojure} Hickey, Rich: Clojure
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
\bibitem{Midje} Marick, Brian: Midje
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
\bibitem{Contact} Sagan, Carl: Contact
\bibitem{Propositions as Types} Wadler, Philip.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines

>>>>

\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, Warp Records, 1994.
\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel, \textit{The Garden of Forking Paths}, 1941.
\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Ser}, 1963.
\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
\bibitem{Contact} Sagan, Carl: Contact, 1985.
\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{CACM}, 2015.
\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
